# 1.Write a R program to get the first 10 Fibonacci numbers.


```{r}
fib_func <- function(){
  fib <- 0:9
  for (i in 3:10) {fib[i] <- fib[i - 2] + fib[i - 1]}
  return(fib)
}
fib_func()
```



# 2.Read a .CSV File and assign the values to a data frame.

# Select a particular row/column and change the value to NA.

# Using the IMPUTE function, replace the value of the row with mean. 

```{r}
library(e1071)
df <- read.csv("addresses.csv",header = FALSE)
head(df)
df$V6[4] = NA
head(df)
df[6] <- impute(df[6],what= c("mean"))
head(df)
```

 

# 3.Write a R program to create three vectors a,b,c with 3 integers. 
# Combine the three vectors to become a 3×3 matrix where each  column represents a vector. Print the content of the matrix.

```{r}
matrix_func <- function(){
  x <- c(1,2,3) 
  y <- c(4,5,6) 
  z <- c(7,8,9) 
  return(cbind(x,y,z))}

matrix_func()
```
 

# 4.  Write a R program to create a vector which contains 10 random integer values between -50 and +50.

```{r}
vector_func <- function() {sample(-50:50, 10, replace=TRUE)}
vector_func()
```

