Create a Matrix - Use Matrix Value 1:40

Decide the appropriate Columns & Rows

Show the result for a column ( you can choose any column)

Show the result for a row ( you can choose any row)

Show the result for a row using Modulo operator( Division) where the reminder ==0

Show the result using a column & row combination(Eg, 3rd row, 5th column)



```{r}
mymatrix <- matrix(1:40, nrow = 5, ncol = 8)
mymatrix
mymatrix[, 7]
mymatrix[4,]
mymatrix[5,mymatrix[1,] %% 2 ==0]
mymatrix[3,4]
```
Identify the Data Type
Assign a numeric to a variable
Find the datatype of the variable

Assign a character to a variable

Find the datatype of the variable
```{r}
a <- 5
mode(a)
b <- 'abcd'
mode(b)
```

Identity the Mean & Median for the following
Values ( 14,5,3,22,-8,9,-3,45,12,43,8,6)
Find the Mean

Apply the trim function using 2 (2 numbers from both ends) and find the mean

Find the Median

mylist <- c(14,5,3,22,-8,9,-3,45,12,43,8,6)
mean(mylist)
mean(mylist,trim = 2)
median(mylist)
Find the mode(s) for the following
values ( 3,4,3,5,3,6,7,2,1,2,6,7,8,6)
Run this in the R Studio using R MarkDown and attach your output as a .HTML file in canvas.
```{r}
mylist2 <- c(3,4,3,5,3,6,7,2,1,2,6,7,8,6)
get_mode <- function(x) {
  uq <- unique(x)
  tab <- tabulate(match(x, uq))
  uq[tab == max(tab)]
}
get_mode(mylist2)
```

