# Import the data into R.
# How many observations are there in the dataset?
# How many observations are there with a fire (i.e., area>0)
# How many observations are there with a rain (i.e., rain>0)
# How many observations are there with both a fire and a rain?

```{r}
library(tidyr)
library(readr)
library(dplyr)
df <- read.csv("forestfires.csv")
NROW(df)
NROW(df$area[df$area > 0])
NROW(df$rain[df$rain > 0])
NROW(filter(df,  area > 0 & rain > 0))
```

#  2.Show the columns month, day, area of the all the observations.

```{r}
options(max.print = 1e7)
print(df[c('month','day','area')],)
```
# 3. Show the columns month, day, area of the observations with a fire.

```{r}
print((filter(df[c('month','day','area')],  area > 0)))
```
 

# 4.How large are the five largest fires (i.e., having largest area)

#      a.What are the corresponding month, temp, RH,wind, rain area?

#      b.Add one column to the data indicating whether a fire occurred for each   observation 

```{r}
a <- df
a[c('month', 'temp', 'RH','wind', 'rain', 'area')]  %>% slice_max(area, n = 5)
df <- df %>%
  mutate(fire_occurred = ifelse(area > 0, TRUE,FALSE))
tail(df,10)
```
 

# 5.  5.Create the following to display the outliers from the below vector.

#    -plot 

#   - boxplot

# Also mention the numbers that are outliers in this vector.

#  (1,2,50,45,67,200,230,55,56,49)

```{r}
v <- c(1,2,50,45,67,200,230,55,56,49)
plot(v)
boxplot(v)
Q1 <- quantile(v, .25)
Q3 <- quantile(v, .75)
IQR <- IQR(v)
normal_numbers <- subset(v, v > (Q1 - 1.5 * IQR) & v < (Q3 + 1.5 * IQR))
cat("Outliers: ", setdiff(v, normal_numbers))
```
# 6. Using the dplyr approach, perform the following actions from 'iris'

#  a) select the columns  Sepal.Length, Sepal.Width, Petal.Length,Petal.Width

# b) filter the iris data for Species = "setosa" or "virginica"

```{r}
library(datasets)
data('iris')
iris %>%
  select(Sepal.Length, Sepal.Width, Petal.Length,Petal.Width)
iris %>%
  filter(Species == "setosa" | Species == "virginica")
```
 
 